Supporting Information: Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-04-30 Ben_Manuscripts/transport/cover_letter.tex
Cover letter for J. Phys. Chem. B.

	\noindent October 10th, 2018\\

@@

	We are submitting ``Understanding the Nanoscale Structure of Inverted Hexagonal 
	Phase Lyotropic Liquid Crystal Polymer Membranes'' by Benjamin J. Coscia, Joseph
	Yelk, Matthew A. Glaser, Douglas L. Gin, Xunda Feng, and Michael R. Shirts, for
	consideration for publication as an Article in the Journal of Physical Chemistry
	B. We expect this work to be of significant interest to researchers who study 
	nanostructured polymer membranes for aqueous separations.

	This article examines the atomistic structure of an inverted hexagonal phase 
	self-assembled lyotropic liquid crystal (LLC) polymer membrane. To create these
	materials, liquid crystal (LC) monomers self-assemble into ordered, uniform-sized
	and hexagonally-packed nanopores. The nm-sized pore centers are charged and hydrophilic 
	in nature which makes this type of membrane useful for highly selective aqueous 
	separations of small solutes. By tuning the shape, size and chemical functionality
	of LC monomers, one could intelligently design the pore environment. However, our 
	current understanding of the nanoscopic pore structure is not yet adequate for us to
	be able to controllably design membranes for solute-specific separations.

	In this paper, we used molecular dynamics (MD) simulations to model an
	experimentally characterized LLC polymer membrane and learn about its detailed
	atomistic structure. We simulated XRD patterns from the MD simulation trajectories
	for comparison to experimental 2D wide-angle X-ray scattering (WAXS) and 1D 
	small-angle X-ray scattering patterns. We found that 5 columns of stacked LLC 
	monomers are likely to pack around the hydrophilic core of each pore. These 
	columns likely move independently of each other	over time scales that we can not
	simulate. Some of the structure previously attributed to monomer tail tilt is 
	likely instead due to ordered tail packing. Although the system studied	has been
	reported as ``dry'', small amounts of water appear necessary to fully reproduce 
	all features from the experimental 2D-WAXS pattern due to asymmetries introduced 
	by hydrogen bonds between the LLC monomer head groups and water molecules. 
	Finally, we explored the composition and structure of the nanopores, showing there is 
	composition gradient rather than an abrupt partition between the hydrophilic and
	hydrophobic regions. The clearer picture of the nanoscopic structure
	of these membranes provided in this study will enable a better understanding of the
	mechanisms of small molecule transport within these nanopores. \\

@@

	\noindent Michael R. Shirts \\
    \noindent Benjamin J. Coscia \\
    \noindent Joseph Yelk \\
    \noindent Matthew A. Glaser
    \noindent Douglas L. Gin \\
    \noindent Xunda Feng \\

>>>>

	\noindent May 3\textsuperscript{rd}, 2019\\

@@

	\newcommand{\ManuscriptTitle}{Chemically Selective Transport in a Cross-linked 
	H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}

	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia and Michael R. Shirts, for
	consideration for publication as an Article in the Journal of Physical Chemistry
	B. We expect this work to be of significant interest to researchers who study 
	nanostructured polymer membranes for aqueous separations.

	In this article, we use molecular dynamics (MD) simulations in order to observe 
	transport of small solutes in an inverted hexagonal (H\textsubscript{II}) phase 
	self-assembled lytropic liquid crystal (LLC) polymer membrane. Recently, we 
	published our first article on this subject in which we built and characterized
	an atomistic molecular model of an LLC membrane that is maximally consistent with experimental
	observations. By observing transport of solutes within a similar model, we can 
	learn the optimal ways to tune the shape, size and chemical functionality
	of LC monomers in order to intelligently design the pore environment and facilitate
	solute-specific separations.

	In this work, we observe and quantify transport of water, sodium and 20 small
	polar solutes within the pores of our atomistic H\textsubscript{II} phase LLC membrane
	model. In general, all solutes exhibit subdiffusive transport behavior
	characterized by intermittent hops between long periods of entrapment. However, 
	due the pores' inhomogeneous architecture, we observed 3 different mechanisms
	of entrapment. First, solutes can diffuse out of the pores and become entangled 
	between tails. Second, many of the solutes are capable of donating hydrogen bonds
	to monomer head groups for extended periods of time. Finally, solutes can associate
	with monomer head group counter-ions within nanopores. Each solute is influenced 
	by each mechanism to varying degrees dependent on its size and chemical 
	functionality. We begin our discussion with a broad description of these mechanisms
	in the context of all solutes before restricting the discussion to more detailed 
	analyses of subsets of chemically-similar solutes.

@@

	\noindent Michael R. Shirts \\
	\noindent Benjamin J. Coscia \\
